A Survey of Exoskeleton Control (Draft 1.1)

### 2015-09-17 paper.tex
more updates

@@

@@

@@

@@

Similar to counterbalancing or physical gravity compensation, except done
with exoskeleton actuators to cancel exoskeleton weight (but not inertia).
A simple formulation is:
\begin{equation}
\mJ^{\tr} (m\vg)
\end{equation}
where $\mJ$ is a Jacobian matrix, $m$ is the weight of the exoskeleton,
and $\vg$ is the gravity vector. 
Operator relies on mechanical backdrivability to drive
exokeleton to do task.

@@

@@

This is how the Sarcos WEAR exoskeleton works.

@@

@@

Sarcos WEAR
http://www.army-technology.com/features/featuremilitary-exoskeletons-uncovered-ironman-suits-a-concrete-possibility
http://www.robaid.com/bionics/raytheons-second-generation-exoskeleton-xos-2.htm

@@

Cyberdyne: HAL 2000 up to at least HAL 5
http://www.computerweekly.com/photostory/2240108388/Photos-Cyberdyne-Hal-robotic-exoskeleton-to-help-paralyzed/7/Japan-beats-the-US-to-it-Cyberdyne-Hal-robotic-exoskeleton-to-help-paralyzed
http://spectrum.ieee.org/robotics/medical-robots/exoskeletons-are-on-the-march
http://www.dailymail.co.uk/sciencetech/article-2384930/Robotic-exoskeleton-help-rehabilitate-disabled-people-passes-safety-tests--paving-way-sale-UK.html

@@

@@

MIT exo
http://biomech.media.mit.edu/portfolio_page/load-bearing-exoskeleton-for-walking/
http://www.technovelgy.com/ct/Science-Fiction-News.asp?NewsNum=1205

Honda (Stride Management Assist (SMA))
http://www.slashgear.com/honda-demo-walking-assist-exoskeleton-for-elderly-disabled-2211295/
http://singularityhub.com/2010/09/13/hondas-exoskeletons-help-you-walk-like-asimo-video/

REX exoskeleton
http://www.gizmag.com/rex-robotic-exoskeleton/15736/pictures
http://www.stripes.com/news/exoskeleton-could-benefit-troops-with-spinal-cord-injuries-1.113657
http://www.funis2cool.com/cool/rex-the-robotic-exoskeleton-could-change-the-lives-of-disabled-people.html

@@

The RoboKnee: an exoskeleton for enhancing strength and endurance during
walking
JE Pratt, BT Krupp, CJ Morse… - … and Automation, 2004. …, 2004 -
ieeexplore.ieee.org

>>>>

\newcommand{\gc}{{\mbox {GravityCompensation}}}

@@

\subsection{What operator-exoskeleton contact forces are acceptable?}

@@

The human and exoskeleton limbs are typically connected to each
other with straps or padding. These connections typically have substantial
compliance and play, and may or may not have appropriate damping.
Typically the human and the exoskeleton do not move the same way:
pose, and linear and angular velocities and accelerations are not the same.

@@

Stability proofs of any of these methods should be viewed extremely skeptically due
to the unmodeled operator-exoskeleton and exoskeleton-world contact dynamics, 
actuator unmodeled dynamics, joint play and structural deformation, controller
time delays which are typically ignored, especially in proofs involving
passivity arguments or Lyapunov functions.

@@

Similar to counterbalancing or physical gravity compensation, except done
with exoskeleton actuators to cancel exoskeleton weight (but not inertia).
A simple formulation is:
\begin{equation}
\vtau = \mJ^{\tr} (m\vg)
\end{equation}
where $\vtau$ are the exoskeleton joint torques, 
$\mJ$ is a Jacobian matrix, $m$ is the weight of the exoskeleton,
and $\vg$ is the gravity vector. 
Operator relies on mechanical backdrivability to drive
exokeleton to do task.

@@

The major drawback of impedance/ admittance control
is that a predefined trajectory or a predefined point must be
assigned as a desired value.[06990981] NOT REALLY TRUE, SEE INVERSE DYNAMICS.

@@

This is how the Sarcos XOS/WEAR exoskeleton works.

\begin{equation}
\dot{\vq} = \mJ^{-1} (\mK_1 \vf)
\end{equation}
\begin{equation}
\vtau = \mK_2 \dot{\vq} + \gc
\end{equation}
where $\dot{\vq}$ are the exoskeleton joint velocities,
$\mJ$ is a Jacobian matrix, $\mK_1$ is a gain matrix,
$\vf$ is the operator-exoskeleton force, 
$\vtau$ is the exoskeleton joint torques, $\mK_2$ is a gain matrix,
and $\gc$ is gravity compensation.
[06990981]

Inverting a Jacobian matrix is problematic when the Jacobian matrices are
near singular, which is common in human gait and manipulation.
Using a fixed or gain scheduled gain matrix may make more sense.
\begin{equation}
\dot{\vq} = \mK_3 \vf
\end{equation}

@@

E. Guizzo and H. Goldstein, "The rise of the body bots [robotic
exoskeletons]," Spectrum, IEEE, vol. 42, pp. 50-56, 2005.

@@

Sarcos XOS/WEAR
http://www.army-technology.com/features/featuremilitary-exoskeletons-uncovered-ironman-suits-a-concrete-possibility
http://www.robaid.com/bionics/raytheons-second-generation-exoskeleton-xos-2.htm

@@

Cyberdyne: HAL 2000 up to at least HAL 5
http://www.computerweekly.com/photostory/2240108388/Photos-Cyberdyne-Hal-robotic-exoskeleton-to-help-paralyzed/7/Japan-beats-the-US-to-it-Cyberdyne-Hal-robotic-exoskeleton-to-help-paralyzed
http://spectrum.ieee.org/robotics/medical-robots/exoskeletons-are-on-the-march
http://www.dailymail.co.uk/sciencetech/article-2384930/Robotic-exoskeleton-help-rehabilitate-disabled-people-passes-safety-tests--paving-way-sale-UK.html
H. Kawamoto, S. Lee, S. Kanbe, and Y. Sankai, "Power assist method
for HAL-3 using EMG-based feedback controller," in Systems, Man
and Cybernetics, 2003. IEEE International Conference on, 2003, pp.
1648-1653.

@@

RoboKnee
J. E. Pratt, B. T. Krupp, C. J. Morse, and S. H. Collins, "The
RoboKnee: an exoskeleton for enhancing strength and endurance
during walking," in Robotics and Automation, 2004. Proceedings.
ICRA'04. 2004 IEEE International Conference on, 2004, pp. 2430-
2435.

@@

MIT exo
http://biomech.media.mit.edu/portfolio_page/load-bearing-exoskeleton-for-walking/
http://www.technovelgy.com/ct/Science-Fiction-News.asp?NewsNum=1205
C. J. Walsh, K. Endo, and H. Herr, "A quasi-passive leg exoskeleton
for load-carrying augmentation," International Journal of Humanoid
Robotics, vol. 4, pp. 487-506, 2007.

Honda (Stride Management Assist (SMA))
http://www.slashgear.com/honda-demo-walking-assist-exoskeleton-for-elderly-disabled-2211295/
http://singularityhub.com/2010/09/13/hondas-exoskeletons-help-you-walk-like-asimo-video/
Honda Walking Assist Device
Y. Ikeuchi, J. Ashihara, Y. Hiki, H. Kudoh, and T. Noda, "Walking
assist device with bodyweight support system," in Intelligent Robots
and Systems, 2009. IROS 2009. IEEE/RSJ International Conference on,
2009, pp. 4073-4079.

REX exoskeleton
http://www.rexbionics.com/
http://www.gizmag.com/rex-robotic-exoskeleton/15736/pictures
http://www.stripes.com/news/exoskeleton-could-benefit-troops-with-spinal-cord-injuries-1.113657
http://www.funis2cool.com/cool/rex-the-robotic-exoskeleton-could-change-the-lives-of-disabled-people.html

@@
